External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
add

\begin{figure*}\vspace{-0.1in}
\centering
\includegraphics[width=0.85\linewidth]{Flowchart2.png}
\vspace{-2mm}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-1mm}
\label{fig2}
\end{figure*}

@@

We employ an alternating iterative approach to solve the optimization problem (\ref{equ4}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}$ as follows:
\vspace{2mm}\\
\textbf{Updating Sparse Coefficient}: Given the orthogonal dictionary $\textbf{D}^{(t)}$, we update each sparse coding vector $\bm{\alpha}_{n,m}$ by solving
\vspace{-3mm}
\begin{equation}\label{equ7}\vspace{-3mm}
\begin{split}
\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}^{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
\end{split}
\end{equation}
Since dictionary $\mathbf{D}^{(t)}$ is orthogonal, the problems (\ref{equ7}) has a closed-form solution
\vspace{-2mm}
\begin{equation}\label{equ8}\vspace{-2mm}
\bm{\alpha}_{n,m}^{(t)}= \text{sgn}((\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|(\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m}|-\bm{\lambda},\mathbf{0}),
\end{equation}
where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.\ The detailed derivation of Eq. (\ref{equ8}) can be found in the supplementary file.
\vspace{2mm}\\
\textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\bm{\alpha}_{n,m}^{(t)}$, we update the internal sub-dictionary by solving
\vspace{-2mm}
\begin{equation}\label{equ9} \vspace{-2mm}
\begin{split}
\textbf{D}_{\text{I}}^{(t+1)}
:
&
=
\argmin_{\textbf{D}_{\text{I}}}
\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
\\
&
=
\argmin_{\textbf{D}_{\text{I}}}
\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
\\
s.t.
\quad
\mathbf{D}
&
=
[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}],\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{I}_{r},\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{0},
\end{split}
\end{equation}
where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$. The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{r\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively. According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
\vspace{-1mm}
\begin{equation}\label{equ10}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}(\mathbf{A}_{i}^{(t)})^{\top}
=
\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}.
\end{equation}
The orthogonality of internal dictionary $\mathbf{D}_{i}^{(t+1)}$ can be checked by 
$(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$.

>>>>

\begin{figure*}\vspace{-0.1in}
\centering
\includegraphics[width=0.85\linewidth]{Flowchart3.png}
\vspace{-2mm}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-3mm}
\label{fig2}
\end{figure*}

@@

We employ an alternating iterative approach to solve the optimization problem (\ref{equ4}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}$ as follows:
\vspace{2mm}\\
\textbf{Updating Sparse Coefficient}: Given the orthogonal dictionary $\textbf{D}^{(t)}$, we update each sparse coding vector $\bm{\alpha}_{n,m}$ by solving
\vspace{-3mm}
\begin{equation}\label{equ7}\vspace{-3mm}
\begin{split}
\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}^{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
\end{split}
\end{equation}
Since dictionary $\mathbf{D}^{(t)}$ is orthogonal, the problems (\ref{equ7}) has a closed-form solution
\vspace{-2mm}
\begin{equation}\label{equ8}\vspace{-2mm}
\bm{\alpha}_{n,m}^{(t)}= \text{sgn}((\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|(\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m}|-\bm{\lambda},\mathbf{0}),
\end{equation}
where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.\ The detailed derivation of Eq. (\ref{equ8}) can be found in the supplementary file.
\vspace{2mm}\\
\textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\bm{\alpha}_{n,m}^{(t)}$, we update the internal sub-dictionary by solving
\vspace{-2mm}
\begin{equation}\label{equ9} \vspace{-2mm}
\begin{split}
\textbf{D}_{\text{I}}^{(t+1)}
:
&
=
\argmin_{\textbf{D}_{\text{I}}}
\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
\\
&
=
\argmin_{\textbf{D}_{\text{I}}}
\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
\\
s.t.
\quad
\mathbf{D}
&
=
[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}],\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{I}_{r},\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{0},
\end{split}
\end{equation}
where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$. The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{r\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively. According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
\vspace{-1mm}
\begin{equation}\label{equ10}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{\text{E}}\mathbf{D}_{\text{E}}^{\top})\mathbf{Y}(\mathbf{A}_{\text{I}}^{(t)})^{\top}
=
\mathbf{U}_{\text{I}}\mathbf{S}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}.
\end{equation}
The orthogonality of internal dictionary $\mathbf{D}_{\text{I}}^{(t+1)}$ can be checked by 
$(\mathbf{D}_{\text{I}}^{(t+1)})^{\top}(\mathbf{D}_{\text{I}}^{(t+1)})=\mathbf{V}_{\text{I}}\mathbf{U}_{\text{I}}^{\top}\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}=\mathbf{I}_{r}$.
